---
title: "ML_Courseproject"
output: html_document
---

This document contains my solution for the machine learning course project
```{r echo=FALSE, warning=FALSE} 
library(caret)
load("ws_courseproject.RData")
```

A first summary of the data shows, that many variables have a lot of NA or other values., so I collect all them and exclude them from further analysis

```{r} 
summary(train_set)
```

I collect all the ones with many NA and exclude them from further analysis. Furthermore I already exclude Username and the timestamp coz i assume that there should be no systematic influence of Username or timestamp on the classification. But i did not check this, maybe for some names that indicate a nationality it could make sense.


```{r} 
#too many NA
alotNAandexkl <- c("max_roll_belt","max_picth_belt","min_roll_belt","min_pitch_belt","amplitude_roll_belt","amplitude_pitch_belt",
                   "var_total_accel_belt","avg_roll_belt","stddev_roll_belt","var_roll_belt","avg_pitch_belt","stddev_pitch_belt",
                   "var_pitch_belt","avg_yaw_belt","stddev_yaw_belt","var_yaw_belt","total_accel_arm","avg_roll_arm","stddev_roll_arm",
                   "var_roll_arm","avg_pitch_arm","stddev_pitch_arm","var_pitch_arm","avg_yaw_arm","stddev_yaw_arm","var_yaw_arm",
                   "max_roll_arm","max_picth_arm","max_yaw_arm","min_roll_arm","min_pitch_arm","min_yaw_arm","amplitude_roll_arm",
                   "amplitude_pitch_arm","amplitude_yaw_arm","max_roll_dumbbell", "var_accel_dumbbell","avg_roll_dumbbell","var_roll_dumbbell",
                   "min_roll_forearm","var_roll_forearm","avg_pitch_forearm","avg_yaw_forearm", "gyros_forearm_z",
                   "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2","cvtd_timestamp")
withoutNA <- names(train_set)
withoutNA <- withoutNA[!withoutNA %in% alotNAandexkl]
withoutNA
```


Now in an analysis step I aggregate the remaining data by the clases and check the values. I create an identifier telling me if there is a strong
variation between the different categories. I know that I need higher variation to be able to discriminate between the categories.
For this I create an identifier saying that i keep only the variables or covariates that with a variation SD/MEAN *100 of more then 49% in respect of the mean 

```{r} 
analysis <- aggregate(.~ classe, data=train_set[,withoutNA], mean)
analysis
check <- sapply(analysis[,2:NCOL(analysis)], function(x)  sd(x) /mean(x)*100)
ident <- names(check[check >49])
ident
```

Now I fit the model using linear discriminant analysis

```{r} 
modelFit <- train(train_set$classe~., data = train_set[,ident], method ="lda")
modelFit
```

I create myself again a sample of the training data set to test the prediction of classification quality of the model

```{r} 
set.seed(123)
newTest = createDataPartition(y=train_set$X, p=0.2, list = FALSE)
newTest_set <- train_set[newTest,]
ldclasse <- predict(modelFit,newTest_set[,ident])
confusionMatrix(ldclasse, newTest_set$classe)
```



Final task is to predict the classes for the test set , as can be seen, all 20 data points would be classified in Category A
```{r} 
set.seed(123)
ldclasse <- predict(modelFit,test_set[,ident])
ldclasse
```





